My title

### 2022-03-21 outputs/paper/paper.Rmd
figures updated

---
title: "My title"
author: 
  - Eunkyo Oh
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

# Pick only the necessary columns
gssurvey <- 
  gssurvey |>
  select(age, 
         feelings_life, 
         sex,
         education, 
         own_rent, 
         living_arrangement, 
         self_rated_health, 
         self_rated_mental_health, 
         religion_has_affiliation, 
         income_family, 
         income_respondent)

@@

age vs feelings
sex vs feelings
education vs feelings

>>>>

---
title: "My title"
author: 
  - Eunkyo Oh
thanks: "Code and data are available at: https://github.com/oheunkyo/."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

# Pick only the necessary columns
gssurvey <- 
  gssurvey |>
  select(age, 
         feelings_life, 
         sex,
         self_rated_health, 
         self_rated_mental_health, 
         income_family)

gssurveyagegroup <- 
  gssurvey |> 
  mutate(age_group = 
           case_when(age < 26 ~ "16-25",
                     age < 36 ~ "26-35",
                     age < 46 ~ "36-45",
                     age < 56 ~ "46-55",
                     age < 66 ~ "56-65",
                     age < 76 ~ "66-75",
                     age < 100 ~ ">76"
                     ),
         age_group = factor(age_group,
                            levels = c("16-25",
                                       "26-35",
                                       "36-45",
                                       "46-55",
                                       "56-65",
                                       "66-75",
                                       ">76"
                                       )
                            )
         )

@@

```{r feelingscount, fig.cap="Number of Perceived Feelings on Life Responses", echo = FALSE, warning=FALSE, message=FALSE}
gssurvey |> 
  ggplot(mapping = aes(x = feelings_life)) +
  geom_histogram(bins = 11, fill="aquamarine4") +
  theme_minimal() +
  labs(x = "Feelings on life (ten point scale)",
       y = "Number of respondents") +
  scale_x_continuous(breaks=seq(0, 10, 1))
```

```{r feelingsvssex, fig.cap="Number of Perceived Feelings on Life Responses by Sex", echo = FALSE, warning=FALSE, message=FALSE}
gssurvey |> 
  ggplot(mapping = aes(x = feelings_life, fill = sex)) +
  geom_bar(position = "dodge") +
  theme_minimal() +
  labs(x = "Feelings on life (ten point scale)",
       y = "Number of respondents",
       fill = "Sex") +
  scale_fill_brewer(palette = "Dark2") +
  scale_x_continuous(breaks=seq(0, 10, 1))
```

```{r agecount, fig.cap="Number of Responses by Age Group", echo = FALSE, warning=FALSE, message=FALSE}
gssurveyagegroup |>  
  ggplot(mapping = aes(x = age_group, fill = feelings_life)) +
  geom_bar(fill="aquamarine4") +
  theme_minimal() + 
  labs(x = "Age groups",
       y = "Number of respondents")
```

```{r averagebyage, echo=FALSE, warning=FALSE, message=FALSE}
# making a new data to find proportions of people per location
summary_gss <- 
  gssurveyagegroup |> 
    group_by(age_group) |> 
    summarise(num = n(), average = mean(feelings_life, na.rm = TRUE))

# Creating a table 
summary_gss |>
    kable(
      caption = "Mean Feeling of Life by Age Group",
      col.names = c("Age Group", 
                    "Number of Respondents", 
                    "Average Feeling of Life"),
      digits = 1,
      booktabs = TRUE, 
      linesep = ""
    )
```

```{r incomevsfeelings, fig.cap="Number of Perceived Feelings on Life Responses by Household Income", echo = FALSE, warning=FALSE, message=FALSE}
level_order <- c('Less than $25,000', '$25,000 to $49,999', 
                 '$50,000 to $74,999', '$75,000 to $99,999', 
                 '$100,000 to $124,999',
                 '$125,000 and more')

gssurvey |>
  filter(income_family %in% level_order) |>
  ggplot(mapping = aes(x = factor(income_family, levels = level_order), y = feelings_life, color = income_family)) +
  geom_jitter() +
  geom_smooth() +
  theme_minimal() +
  labs(x = "Household Income (CAD)",
       y = "Feelings on life (ten point scale)") +
  guides(color="none") +
  scale_fill_brewer(palette = "Dark2") +
  scale_y_continuous(breaks=seq(0, 10, 1))

```{r healthvsfeelings, fig.cap="Self Rated Health versus Feeling on Life and Self Rated Mental Health versus Feeling on Life",echo=FALSE, warning=FALSE, message=FALSE}

library(patchwork)

level_order <- c('Poor', 'Fair', 'Good', 'Very good', 'Excellent')
health <-
  gssurvey |>
  filter(self_rated_health %in% level_order) |>
    ggplot(mapping = aes(x = factor(self_rated_health, level=level_order), 
                         y = feelings_life, color = self_rated_health)) +
    geom_jitter() +
    geom_smooth() +
    theme_minimal() +
    labs(x = "Self rated health (ten point scale)",
         y = "Feelings on life (ten point scale)",
         caption = "Figure 5: Self Rated \n Health versus Feeling on Life") +
    guides(color="none") +
    scale_fill_brewer(palette = "Dark2") +
    scale_y_continuous(breaks=seq(0, 10, 1))

mhealth <-
  gssurvey |>
  filter(self_rated_mental_health %in% level_order) |>
    ggplot(mapping = aes(x = factor(self_rated_mental_health, level=level_order), 
                         y = feelings_life, color = self_rated_mental_health)) +
    geom_jitter() +
    geom_smooth() +
    theme_minimal() +
    labs(x = "Self rated mental health (ten point scale)",
         y = "Feelings on life (ten point scale)",
         caption = "Figure 6: Self Rated Mental \n Health versus Feeling on Life") +
    guides(color="none") +
    scale_fill_brewer(palette = "Dark2") +
    scale_y_continuous(breaks=seq(0, 10, 1))

(health + mhealth)
```
removeed NA and DOn't KNow responses
